How do changes in ex vary between countries?

### 2022-03-04 draft_paper.Rmd

---
title: "How do changes in ex vary between countries?"
author: "Jon Minton"
date: "22/02/2022"
output:
  html_document: default
  word_document: default
---

>>>>

---
title: "How do changes in ex vary between countries?"
author: "Jon Minton, Lucinda Hiam"
date: "22/02/2022"
output:
  word_document: default
  html_document: default
---
